% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Bandersnatch VRF-AD Specification},
  pdfauthor={Davide Galassi; Seyed Hosseini},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Bandersnatch VRF-AD Specification}
\author{Davide Galassi \and Seyed Hosseini}
\date{2 Nov 2024 - Draft 21}

\begin{document}
\maketitle

\newcommand{\G}{\langle G \rangle}
\newcommand{\F}{\mathbb{Z}^*_r}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{abstract}{%
\section{\texorpdfstring{\emph{Abstract}}{Abstract}}\label{abstract}}

This specification delineates the framework for a Verifiable Random
Function with Additional Data (VRF-AD), a cryptographic construct that
augments a standard VRF by incorporating auxiliary information into its
signature. We're going to first provide a specification to extend IETF's
ECVRF as outlined in
\href{https://datatracker.ietf.org/doc/rfc9381}{RFC-9381} {[}1{]}, then
we describe a variant of the Pedersen VRF originally introduced by
\href{https://eprint.iacr.org/2023/002}{BCHSV23} {[}2{]}, which serves
as a fundamental component for implementing anonymized ring signatures
as further elaborated by
\href{https://github.com/davxy/ring-proof-spec}{VG24} {[}3{]}. This
specification provides detailed insights into the usage of these
primitives with Bandersnatch, an elliptic curve constructed over the
BLS12-381 scalar field specified in
\href{https://eprint.iacr.org/2021/1152}{MSZ21} {[}4{]}.

\hypertarget{preliminaries}{%
\section{1. Preliminaries}\label{preliminaries}}

\textbf{Definition}: A \emph{verifiable random function with additional
data (VRF-AD)} can be described with two functions:

\begin{itemize}
\item
  \(Prove(sk,in,ad) \mapsto (out,\pi)\) : from secret key \(sk\), input
  \(in\), and additional data \(ad\) returns a verifiable output \(out\)
  and proof \(\pi\).
\item
  \(Verify(pk,in,ad,out,\pi) \mapsto (0|1)\) : for public key \(pk\),
  input \(in\), additional data \(ad\), output \(out\) and proof \(\pi\)
  returns either \(1\) on success or \(0\) on failure.
\end{itemize}

\hypertarget{vrf-input}{%
\subsection{1.1. VRF Input}\label{vrf-input}}

An arbitrary length octet-string provided by the user and used to
generate some unbiasable verifiable random output.

\hypertarget{vrf-input-point}{%
\subsection{1.2. VRF Input Point}\label{vrf-input-point}}

A point in \(\langle G \rangle\) generated from VRF input octet-string
using the \emph{Elligator 2} \emph{hash-to-curve} algorithm as described
by section 6.8.2 of
\href{https://datatracker.ietf.org/doc/rfc9380}{RFC-9380} {[}5{]}.

\hypertarget{vrf-output-point}{%
\subsection{1.3. VRF Output Point}\label{vrf-output-point}}

A point in \(\langle G \rangle\) generated from VRF input point as:
\(Output \gets sk \cdot Input\).

\hypertarget{vrf-output}{%
\subsection{1.4. VRF Output}\label{vrf-output}}

A fixed length octet-string generated from VRF output point using the
proof-to-hash procedure defined in section 5.2 of
\href{https://datatracker.ietf.org/doc/rfc9381}{RFC-9381}.

The first 32 bytes of the hash output are taken.

\hypertarget{additional-data}{%
\subsection{1.5 Additional Data}\label{additional-data}}

An arbitrary length octet-string provided by the user to be signed
together with the generated VRF output. This data doesn't influence the
produced VRF output.

\hypertarget{challenge-procedure}{%
\subsection{1.6. Challenge Procedure}\label{challenge-procedure}}

Challenge construction mostly follows the procedure given in section
5.4.3 of \href{https://datatracker.ietf.org/doc/rfc9381}{RFC-9381}
{[}1{]} with some tweaks to add additional data.

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(\bar{P} \in \langle G \rangle^n\): Sequence of \(n\) points.
\item
  \(ad \in \Sigma^*\): Additional data octet-string.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(c \in \mathbb{Z}^*_r\): Challenge scalar.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(str_0 \gets \texttt{suite\_string}\;\Vert\;0x02\)
\item
  \(str_i \gets str_{i-1}\;\Vert\;\texttt{point\_to\_string}(P_{i-1}),\ i = 1 \dots n\)
\item
  \(h \gets \texttt{hash}(str_n\;\Vert\;ad\;\Vert\;0x00)\)
\item
  \(c \gets \texttt{string\_to\_int}(h_{0 \dots cLen - 1})\)
\end{enumerate}

With \texttt{point\_to\_string}, \texttt{string\_to\_int} and
\texttt{hash} as defined in section 2.1.

\hypertarget{ietf-vrf}{%
\section{2. IETF VRF}\label{ietf-vrf}}

Based on IETF \href{https://datatracker.ietf.org/doc/rfc9381}{RFC-9381}
which is extended with the capability to sign additional user data
(\(ad\)).

\hypertarget{configuration}{%
\subsection{2.1. Configuration}\label{configuration}}

Configuration is given by following the \emph{``cipher suite''}
guidelines defined in section 5.5 of
\href{https://datatracker.ietf.org/doc/rfc9381}{RFC-9381}.

\begin{itemize}
\item
  \texttt{suite\_string} = \texttt{"Bandersnatch\_SHA-512\_ELL2"}.
\item
  The EC group \(\langle G \rangle\) is the prime subgroup of the
  Bandersnatch elliptic curve, in Twisted Edwards form, with finite
  field and curve parameters as specified in
  \href{https://eprint.iacr.org/2021/1152}{MSZ21}. For this group,
  \texttt{fLen} = \texttt{qLen} = \(32\) and \texttt{cofactor} = \(4\).
\item
  The prime subgroup generator \(G \in \langle G \rangle\) is defined as
  follows:
  \[_{G_x = 18886178867200960497001835917649091219057080094937609519140440539760939937304}\]
  \[_{G_y = 19188667384257783945677642223292697773471335439753913231509108946878080696678}\]
\item
  \texttt{cLen} = 32.
\item
  The public key generation primitive is \(pk = sk \cdot G\), with
  \(sk\) the secret key scalar and \(G\) the group generator. In this
  cipher suite, the secret scalar \texttt{x} is equal to the secret key
  \texttt{sk}.
\item
  \texttt{encode\_to\_curve\_salt} = \texttt{""} (empty - no salt)
\item
  The \texttt{ECVRF\_nonce\_generation} function is specified in section
  5.4.2.2 of \href{https://datatracker.ietf.org/doc/rfc9381}{RFC-9381}.
\item
  The \texttt{int\_to\_string} function encodes into the 32 bytes little
  endian representation.
\item
  The \texttt{string\_to\_int} function decodes from the 32 bytes little
  endian representation eventually reducing modulo the prime field
  order.
\item
  The \texttt{point\_to\_string} function converts a point in
  \(\langle G \rangle\) to an octet-string using compressed form. The
  \(y\) coordinate is encoded using \texttt{int\_to\_string} function
  and the most significant bit of the last octet is used to keep track
  of \(x\) sign. This implies that \texttt{ptLen\ =\ flen\ =\ 32}.
\item
  The \texttt{string\_to\_point} function converts an octet-string to a
  point on \(\langle G \rangle\). The string most significant bit is
  removed to recover the \(x\) coordinate as function of \(y\), which is
  first decoded from the rest of the string using
  \texttt{int\_to\_string} procedure. This function MUST outputs
  ``INVALID'' if the octet-string does not decode to a point on the
  prime subgroup \(\langle G \rangle\).
\item
  The hash function \texttt{hash} is SHA-512 as specified in
  \href{https://datatracker.ietf.org/doc/rfc6234}{RFC-6234} {[}6{]},
  with \texttt{hLen} = 64.
\item
  The \texttt{ECVRF\_encode\_to\_curve} function uses \emph{Elligator2}
  method as described in section 6.8.2 of
  \href{https://datatracker.ietf.org/doc/rfc9380}{RFC-9380} and in
  section 5.4.1.2 of
  \href{https://datatracker.ietf.org/doc/rfc9381}{RFC-9381}, with
  parametrized with \texttt{h2c\_suite\_ID\_string} =
  \texttt{"Bandersnatch\_XMD:SHA-512\_ELL2\_RO\_"} and domain separation
  tag \texttt{DST\ =\ "ECVRF\_"} \(\Vert\)
  \texttt{h2c\_suite\_ID\_string} \(\Vert\) \texttt{suite\_string}.
\end{itemize}

\hypertarget{prove}{%
\subsection{2.2. Prove}\label{prove}}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(x \in \mathbb{Z}^*_r\): Secret key
\item
  \(I \in \langle G \rangle\): VRF input point
\item
  \(ad \in \Sigma^*\): Additional data octet-string.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(O \in \langle G \rangle\): VRF output point
\item
  \(\pi \in (\mathbb{Z}^*_r, \mathbb{Z}^*_r)\): Schnorr-like proof
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(O \gets x \cdot I\)
\item
  \(Y \gets x \cdot G\)
\item
  \(k \gets \texttt{nonce}(x, I)\)
\item
  \(c \gets \texttt{challenge}(Y, I, O, k \cdot G, k \cdot I, ad)\)
\item
  \(s \gets k + c \cdot x\)
\item
  \(\pi \gets (c, s)\)
\end{enumerate}

\textbf{Externals}:

\begin{itemize}
\tightlist
\item
  \(\texttt{nonce}\): refer to section 5.4.2.2 of
  \href{https://datatracker.ietf.org/doc/rfc9381}{RFC-9381}.
\item
  \(\texttt{challenge}\): refer to section 1.6 of this specification.
\end{itemize}

\hypertarget{verify}{%
\subsection{2.3. Verify}\label{verify}}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(Y \in \langle G \rangle\): Public key
\item
  \(I \in \langle G \rangle\): VRF input point
\item
  \(ad \in \Sigma^*\): Additional data octet-string.
\item
  \(O \in \langle G \rangle\): VRF output point
\item
  \(\pi \in (\mathbb{Z}^*_r, \mathbb{Z}^*_r)\): Schnorr-like proof
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\theta \in \{ \top, \bot \}\): \(\top\) if proof is valid, \(\bot\)
  otherwise.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \((c, s) \gets \pi\)
\item
  \(U \gets s \cdot G - c \cdot Y\)
\item
  \(V \gets s \cdot I - c \cdot O\)
\item
  \(c' \gets \texttt{challenge}(Y, I, O, U, V, ad)\)
\item
  \(\theta \gets \top \text{ if } c = c' \text{ else } \bot\)
\end{enumerate}

\textbf{Externals}:

\begin{itemize}
\tightlist
\item
  \(\texttt{challenge}\): as defined for \(Prove\)
\end{itemize}

\hypertarget{pedersen-vrf}{%
\section{3. Pedersen VRF}\label{pedersen-vrf}}

Pedersen VRF resembles IETF EC-VRF but replaces the public key with a
Pedersen commitment to the secret key, which makes this VRF useful in
anonymized ring proofs.

The scheme proves that the output has been generated with a secret key
associated with a blinded public key (instead of the public key). The
blinded public key is a cryptographic commitment to the public key, and
it can be unblinded to prove that the output of the VRF corresponds to
the public key of the signer.

This specification mostly follows the design proposed by
\href{https://eprint.iacr.org/2023/002}{BCHSV23} {[}2{]} in section 4
with some details about blinding base point value and challenge
generation procedure.

\hypertarget{configuration-1}{%
\subsection{3.1. Configuration}\label{configuration-1}}

Pedersen VRF is configured for prime subgroup \(\langle G \rangle\) of
Bandersnatch elliptic curve \(E\), in Twisted Edwards form, defined in
\href{https://eprint.iacr.org/2021/1152}{MSZ21} {[}4{]} with
\emph{blinding base} \(B \in \langle G \rangle\) defined as follows:
\[_{B_x = 38168223498318911142286050663287153682718239172559550124349816380809451936776}\]
\[_{B_y = 13115037257460794964097483333460798982818600992000859876014531380573406267597}\]

For all the other configurable parameters and external functions we
adhere as much as possible to the Bandersnatch cipher suite for IETF VRF
described in section 2.1 of this specification.

\hypertarget{prove-1}{%
\subsubsection{3.2. Prove}\label{prove-1}}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(x \in \mathbb{Z}^*_r\): Secret key
\item
  \(b \in \mathbb{Z}^*_r\): Secret blinding factor
\item
  \(I \in \langle G \rangle\): VRF input point
\item
  \(ad \in \Sigma^*\): Additional data octet-string.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(O \in \langle G \rangle\): VRF output point
\item
  \(\pi \in (\langle G \rangle, \langle G \rangle, \langle G \rangle, \mathbb{Z}^*_r, \mathbb{Z}^*_r)\):
  Pedersen proof
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(O \gets x \cdot I\)
\item
  \(k \gets \texttt{nonce}(x, I)\)
\item
  \(k_b \gets \texttt{nonce}(b, I)\)
\item
  \(\bar{Y} \gets x \cdot G + b \cdot B\)
\item
  \(R \gets k \cdot G + k_b \cdot B\)
\item
  \(O_k \gets k \cdot I\)
\item
  \(c \gets \texttt{challenge}(\bar{Y}, I, O, R, O_k, ad)\)
\item
  \(s \gets k + c \cdot x\)
\item
  \(s_b \gets k_b + c \cdot b\)
\item
  \(\pi \gets (\bar{Y}, R, O_k, s, s_b)\)
\end{enumerate}

\hypertarget{verify-1}{%
\subsection{3.3. Verify}\label{verify-1}}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(I \in \langle G \rangle\): VRF input point
\item
  \(ad \in \Sigma^*\): Additional data octet-string.
\item
  \(O \in \langle G \rangle\): VRF output point
\item
  \(\pi \in (\langle G \rangle, \langle G \rangle, \langle G \rangle, \mathbb{Z}^*_r, \mathbb{Z}^*_r)\):
  Pedersen proof
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\theta \in \{ \top, \bot \}\): \(\top\) if proof is valid, \(\bot\)
  otherwise.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \((\bar{Y}, R, O_k, s, s_b) \gets \pi\)
\item
  \(c \gets \texttt{challenge}(\bar{Y}, I, O, R, O_k, ad)\)
\item
  \(\theta_0 \gets \top \text{ if } O_k + c \cdot O = I \cdot s \text{ else } \bot\)
\item
  \(\theta_1 \gets \top \text{ if } R + c \cdot \bar{Y} = s \cdot G + s_b \cdot B \text{ else } \bot\)
\item
  \(\theta = \theta_0 \land \theta_1\)
\end{enumerate}

\hypertarget{ring-vrf}{%
\section{4. Ring VRF}\label{ring-vrf}}

Anonymized ring VRF based of {[}Pedersen VRF{]} and Ring Proof as
proposed in \href{https://github.com/davxy/ring-proof-spec}{VG24}.

\hypertarget{configuration-2}{%
\subsection{4.1. Configuration}\label{configuration-2}}

Ring proof is configured to work together with Pedersen VRF as presented
in this specification.

The following configuration should be applied to specialize
\href{https://github.com/davxy/ring-proof-spec}{VG24} in order to
instance the concrete scheme.

\begin{itemize}
\item
  \textbf{Groups and Fields}:

  \begin{itemize}
  \tightlist
  \item
    \(\mathbb{G_1}\): BLS12-381 prime order subgroup.
  \item
    \(\mathbb{F}\): BLS12-381 scalar field.
  \item
    \(J\): Bandersnatch curve defined over \(\mathbb{F}\).
  \end{itemize}
\item
  \textbf{Polynomial Commitment Scheme}

  \begin{itemize}
  \tightlist
  \item
    KZG with SRS derived from
    \href{https://zfnd.org/conclusion-of-the-powers-of-tau-ceremony}{Zcash}
    powers of tau ceremony.
  \end{itemize}
\item
  \textbf{Fiat-Shamir Transform}

  \begin{itemize}
  \tightlist
  \item
    \href{https://crates.io/crates/ark-transcript}{\texttt{ark-transcript}}.
  \item
    Begin with empty transcript and ``ring-proof'' label.
  \item
    Push \(R\) to the transcript after instancing.
  \item
    TODO: Specify the order and how parameters are added to the
    transcript as we progress the protocol.
  \end{itemize}
\item
  Accumulator seed point in Twisted Edwards form:
  \[_{\text{S}_x = 40466805124442823009206085742433914639946090367156029186462738700056462095646}\]
  \[_{\text{S}_y = 34469198087286762951014035959822415945315930553941756446161542933145938584110}\]

  \begin{itemize}
  \tightlist
  \item
    Compressed:
    \(_{\texttt{0x63c8bc15a50fb4281b9a50a37cbde791377ebe5a7cde71fd7ee545d1f0230a42}}\)
  \end{itemize}
\item
  Padding point in Twisted Edwards form:
  \[_{\square_x = 26690044630372444677440308098946018389016038587388751811165279176488605875833}\]
  \[_{\square_y = 569559155228528470326092120674498621727733902430463954153034712442147510565}\]

  \begin{itemize}
  \tightlist
  \item
    Compressed:
    \(_{\texttt{0xf5399e03f2121ff4c5d33386cdc66d56a6c5132b739f753442f7bda6c7698c03}}\)
  \end{itemize}

  A point with unknown discrete logarithm derived using the
  \texttt{ECVRF\_encode\_to\_curve} function as described in IETF suite
  {[}Configuration{]} section with input the string:
  \texttt{"ring-proof-pad"}.
\item
  Polynomials domain (\(\langle \omega \rangle = \mathbb{D}\))
  generator:
  \[_{\omega = 49307615728544765012166121802278658070711169839041683575071795236746050763237}\]
\item
  \(|\mathbb{D}| = 2048\)
\end{itemize}

\hypertarget{short-weierstrass-form-requirement}{%
\subsubsection{4.1.1. Short Weierstrass Form
Requirement}\label{short-weierstrass-form-requirement}}

The Ring-Proof scheme, as outlined in
\href{https://github.com/davxy/ring-proof-spec}{VG24}, mandates that all
points must be in Short Weierstrass form. Therefore, any point used in
this scheme, whether derived from Twisted Edwards form or otherwise,
must first be converted to Short Weierstrass form. This requirement
applies to both user-related values, such as the ring points used by the
ring public keys, and to configuration points like the accumulator and
padding.

\hypertarget{prove-2}{%
\subsection{4.2. Prove}\label{prove-2}}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(x \in \mathbb{Z}^*_r\): Secret key
\item
  \(P \in ?\): Ring prover
\item
  \(k \in \mathbb{N}_k\): prover public key position within the ring
\item
  \(b \in \mathbb{Z}^*_r\): Secret blinding factor
\item
  \(I \in \langle G \rangle\): VRF input point
\item
  \(ad \in \Sigma^*\): Additional data octet-string.
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(O \in \langle G \rangle\): VRF output point
\item
  \(\pi_p \in (\langle G \rangle, \langle G \rangle, \langle G \rangle, \mathbb{Z}^*_r, \mathbb{Z}^*_r)\):
  Pedersen proof
\item
  \(\pi_r \in ((G_1)^4, (\mathbb{Z}^*_r)^7, G_1, \mathbb{Z}^*_r, G_1, G_1)\):
  Ring proof
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \((O, \pi_p) \gets Pedersen.prove(x, b, k, I, ad)\)
\item
  \(\pi_r \gets Ring.prove(P, b)\)
\end{enumerate}

\hypertarget{verify-2}{%
\subsection{4.3. Verify}\label{verify-2}}

\textbf{Input}:

\begin{itemize}
\tightlist
\item
  \(V \in (G_1)^3\): Ring verifier (pre-processed commitment).
\item
  \(I \in \langle G \rangle\): VRF input point.
\item
  \(O \in G\): VRF output point.
\item
  \(ad \in \Sigma^*\): Additional data octet-string.
\item
  \(\pi_p \in (\langle G \rangle, \langle G \rangle, \langle G \rangle, \mathbb{Z}^*_r, \mathbb{Z}^*_r)\):
  Pedersen proof
\item
  \(\pi_r \in ((G_1)^4, (\mathbb{Z}^*_r)^7, G_1, \mathbb{Z}^*_r, G_1, G_1)\):
  Ring proof
\end{itemize}

\textbf{Output}:

\begin{itemize}
\tightlist
\item
  \(\theta \in \{ \top, \bot \}\): \(\top\) if proof is valid, \(\bot\)
  otherwise.
\end{itemize}

\textbf{Steps}:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \(\theta_0 = Pedersen.verify(I, ad, O, \pi_p)\)
\item
  \((\bar{Y}, R, O_k, s, s_b) \gets \pi_p\)
\item
  \(\theta_1 = Ring.verify(V, \pi_r, \bar{Y})\)
\item
  \(\theta \gets \theta_0 \land \theta_1\)
\end{enumerate}

\hypertarget{appendix-a}{%
\section{Appendix A}\label{appendix-a}}

The test vectors in this section were generated using code provided at
\href{https://github.com/davxy/ark-ec-vrfs}{\texttt{https://github.com/davxy/ark-ec-vrfs}}.

\hypertarget{a.1.-ietf-vrf-test-vectors}{%
\subsection{A.1. IETF VRF Test
Vectors}\label{a.1.-ietf-vrf-test-vectors}}

Schema:

\begin{verbatim}
sk (x): Secret key,
pk (Y): Public key,
in (alpha): Input octet-string,
ad: Additional data octet-string,
h (I): VRF input point,
gamma (O): VRF output point,
out (beta): VRF output octet string,
proof_c: Proof 'c' component,
proof_s: Proof 's' component,
\end{verbatim}

\hypertarget{vector-1}{%
\subsubsection{Vector 1}\label{vector-1}}

\begin{verbatim}
3d6406500d4009fdf2604546093665911e753f2213570a29521fd88bc30ede18,
a1b1da71cc4682e159b7da23050d8b6261eb11a3247c89b07ef56ccd002fd38b,
-,
-,
c5eaf38334836d4b10e05d2c1021959a917e08eaf4eb46a8c4c8d1bec04e2c00,
e7aa5154103450f0a0525a36a441f827296ee489ef30ed8787cff8df1bef223f,
fdeb377a4ffd7f95ebe48e5b43a88d069ce62188e49493500315ad55ee04d744
..2b93c4c91d5475370e9380496f4bc0b838c2483bce4e133c6f18b0adbb9e4722,
439fd9495643314fa623f2581f4b3d7d6037394468084f4ad7d8031479d9d101,
828bedd2ad95380b11f67a05ea0a76f0c3fef2bee9f043f4dffdddde09f55c01,
\end{verbatim}

\hypertarget{vector-2}{%
\subsubsection{Vector 2}\label{vector-2}}

\begin{verbatim}
8b9063872331dda4c3c282f7d813fb3c13e7339b7dc9635fdc764e32cc57cb15,
5ebfe047f421e1a3e1d9bbb163839812657bbb3e4ffe9856a725b2b405844cf3,
0a,
-,
8c1d1425374f01d86b23bfeab770c60b58d2eeb9afc5900c8b8a918d09a6086b,
60f32f5ad3e9694b82ccc0a735edb2f940f757ab333cc5f7b0a41158b80f574f,
44f3728bc5ad550aeeb89f8db340b2fceffc946be3e2d8c5d99b47c1fce344b3
..c7fcee223a9b29a64fe4a86a9994784bc165bb0fba03ca0a493f75bee89a0946,
8aa1c755a00a6a25bdecda197ee1b60a01e50787bd10aa976133f4c39179330e,
18c74ffd67e6abc658e2d05ecd3101ddc0c33623823f2395538cf8d39e654f12,
\end{verbatim}

\hypertarget{vector-3}{%
\subsubsection{Vector 3}\label{vector-3}}

\begin{verbatim}
6db187202f69e627e432296ae1d0f166ae6ac3c1222585b6ceae80ea07670b14,
9d97151298a5339866ddd3539d16696e19e6b68ac731562c807fe63a1ca49506,
-,
0b8c,
c5eaf38334836d4b10e05d2c1021959a917e08eaf4eb46a8c4c8d1bec04e2c00,
67a348e256d908eb695d15ee0d869efef2bcf9f0fea646e788f967abbc0464dd,
edde0178045133eb03ef4d1ad8b978a56ee80ec4eab8830d6bc6c08003138841
..6657d3c449d9398cc4385d1c8a2bb19bcf61ff086e5a6c477a0302ce270d1abf,
aec4d1cf308cb4cb400190350e69f4fb309255aa738fff5a6ac4ced7538fce03,
54e5d38a76f309ce63ca82465160abd8d75b78805a0b499e60c26436de4a8e01,
\end{verbatim}

\hypertarget{vector-4}{%
\subsubsection{Vector 4}\label{vector-4}}

\begin{verbatim}
b56cc204f1b6c2323709012cb16c72f3021035ce935fbe69b600a88d842c7407,
dc2de7312c2850a9f6c103289c64fbd76e2ebd2fa8b5734708eb2c76c0fb2d99,
73616d706c65,
-,
672e8c7a8e6d3eca67df38f11d50f3d7dbb26fa8e27565a5424e6f8ac4555dcc,
4d3e0524fc59374f1fdad8e471c695469b45ecf69c1de85c6c1230e888dd4cbe,
36127f8aee7c61048984f0a208bf6d334db9dacbeeeef9ff2d17117e81232832
..1462eb3ef602f5911d77ab11f815eb4154ba95c934e414198ef000a61b4de31a,
b72598f235145a377911caa794ba85820173c4c49b7be3b05d847b2c753e0311,
e8e34ad3131388a88eb7f80bd874f3421c378d4ad45911c4bc16e4cdc17b5716,
\end{verbatim}

\hypertarget{vector-5}{%
\subsubsection{Vector 5}\label{vector-5}}

\begin{verbatim}
da36359bf1bfd1694d3ed359e7340bd02a6a5e54827d94db1384df29f5bdd302,
decb0151cbeb49f76f10419ab6a96242bdc87baac8a474e5161123de4304ac29,
42616e646572736e6174636820766563746f72,
-,
4315192d2ce9e52ceb449a6b4da7f7e6636e53592c7f5e236763e21e9bac24c7,
9508104b820469687488d83f729288d9f70fc0523318beff44a47da10d490b3c,
4ee61f3c000544aa48c565e143e05c6501a623bdbf02a0a408b97433660b4907
..715f75890cc0e45cdd7116e3da15b15c3c637782e8e05d05c0d5895e5fe583d1,
ad6af59b4b84f18187c694ef374687d13517cb53508ff9dafa37d0c759e9601c,
4c1269d9d161dabd082fc606af979eca7f6c3ab68e78261dc6fb9fbbb98c9704,
\end{verbatim}

\hypertarget{vector-6}{%
\subsubsection{Vector 6}\label{vector-6}}

\begin{verbatim}
da36359bf1bfd1694d3ed359e7340bd02a6a5e54827d94db1384df29f5bdd302,
decb0151cbeb49f76f10419ab6a96242bdc87baac8a474e5161123de4304ac29,
42616e646572736e6174636820766563746f72,
1f42,
4315192d2ce9e52ceb449a6b4da7f7e6636e53592c7f5e236763e21e9bac24c7,
9508104b820469687488d83f729288d9f70fc0523318beff44a47da10d490b3c,
4ee61f3c000544aa48c565e143e05c6501a623bdbf02a0a408b97433660b4907
..715f75890cc0e45cdd7116e3da15b15c3c637782e8e05d05c0d5895e5fe583d1,
4fa53519bd9d17acae4d1021416557d11b84dd4670b563770c14eb98161eaa08,
0f7f9bee9077427f547e69b919cf8d63823c14b20085fd9516768e0f5e3d3f0e,
\end{verbatim}

\hypertarget{vector-7}{%
\subsubsection{Vector 7}\label{vector-7}}

\begin{verbatim}
35b877a25c394512292b82bdf8468e98eaf03c79c7fc9d53546dadc5fb75b500,
b0e1f208f9d6e5b310b92014ea7ef3011e649dab038804759f3766e01029d623,
42616e646572736e6174636820766563746f72,
1f42,
4315192d2ce9e52ceb449a6b4da7f7e6636e53592c7f5e236763e21e9bac24c7,
6d1dd583bea262323c7dc9e94e57a472e09874e435719010eeafae503c433f16,
09106f062ac07846f3f841f64765527b333575143483855d633f99ccc2e8e306
..e6239ff79a1272cff931e8d0ac6c390328486329118ad40a18b85184da1837ff,
6dbeeab9648505fa6a95de52d611acfbb2febacc58cdc7d0ca45abd8c952ef12,
ce7f4a2354a6c3f97aee6cc60c6aa4c4430b12ed0f0ef304b326c776618d7609,
\end{verbatim}

\hypertarget{a.2.-pedersen-vrf-test-vectors}{%
\subsection{A.2. Pedersen VRF Test
Vectors}\label{a.2.-pedersen-vrf-test-vectors}}

Schema:

\begin{verbatim}
sk (x): Secret key,
pk (Y): Public key,
in (alpha): Input octet-string,
ad: Additional data octet-string,
h (I): VRF input point,
gamma (O): VRF output point,
out (beta): VRF output octet string,
blinding: Blinding factor,
proof_pk_com (Y^-): Public key commitment,
proof_r: Proof 'R' component,
proof_ok: Proof 'O_k' component,
proof_s: Proof 's' component,
proof_sb: Proof 's_b' component
\end{verbatim}

\hypertarget{vector-1-1}{%
\subsubsection{Vector 1}\label{vector-1-1}}

\begin{verbatim}
3d6406500d4009fdf2604546093665911e753f2213570a29521fd88bc30ede18,
a1b1da71cc4682e159b7da23050d8b6261eb11a3247c89b07ef56ccd002fd38b,
-,
-,
c5eaf38334836d4b10e05d2c1021959a917e08eaf4eb46a8c4c8d1bec04e2c00,
e7aa5154103450f0a0525a36a441f827296ee489ef30ed8787cff8df1bef223f,
fdeb377a4ffd7f95ebe48e5b43a88d069ce62188e49493500315ad55ee04d744
..2b93c4c91d5475370e9380496f4bc0b838c2483bce4e133c6f18b0adbb9e4722,
01371ac62e04d1faaadbebaa686aaf122143e2cda23aacbaa4796d206779a501,
ba4107f3bce947c7f61b97efe75d6a20bbea98d6813657d00aa20081befcb325,
d2c7b026c5e44c7174da17e557d4688af333224513bd08794ed87848161a594d,
ac57ce6a53a887fc59b6aa73d8ff0e718b49bd9407a627ae0e9b9e7c5d0d175b,
7dd20b189167b3815c37b10572612491aa799b9275ba378e5e70bf200b43a210,
ace0f2cfa446cbb32b57945f233ebd6b02b5b86d325c8c6901a23f588eaaa70a,
\end{verbatim}

\hypertarget{vector-2-1}{%
\subsubsection{Vector 2}\label{vector-2-1}}

\begin{verbatim}
8b9063872331dda4c3c282f7d813fb3c13e7339b7dc9635fdc764e32cc57cb15,
5ebfe047f421e1a3e1d9bbb163839812657bbb3e4ffe9856a725b2b405844cf3,
0a,
-,
8c1d1425374f01d86b23bfeab770c60b58d2eeb9afc5900c8b8a918d09a6086b,
60f32f5ad3e9694b82ccc0a735edb2f940f757ab333cc5f7b0a41158b80f574f,
44f3728bc5ad550aeeb89f8db340b2fceffc946be3e2d8c5d99b47c1fce344b3
..c7fcee223a9b29a64fe4a86a9994784bc165bb0fba03ca0a493f75bee89a0946,
99ff52abf49d67c4303ac4a8a00984d04c06388f5f836ebd37031f0e76245815,
a663bfbd422eaa3e8abf8023d740d64da2581768a5d8757d5fd4060bd3783aed,
6b6d6288147c9584e4441c1e7aea78b90024f915530c209b27f8cac1bed2c140,
fc8770c209212640742d53e2f40e5c30fffae574f90fdc670ff11a1127586c03,
a09e060423f8faa53d1e16ce0b24cc759ee77c3ceb0c3fe74ba34fb1d9d2a108,
e776fd83c7c92dcb56f0be6975bd5bb10c11a6b5f383099bcc81886ae9e10f17,
\end{verbatim}

\hypertarget{vector-3-1}{%
\subsubsection{Vector 3}\label{vector-3-1}}

\begin{verbatim}
6db187202f69e627e432296ae1d0f166ae6ac3c1222585b6ceae80ea07670b14,
9d97151298a5339866ddd3539d16696e19e6b68ac731562c807fe63a1ca49506,
-,
0b8c,
c5eaf38334836d4b10e05d2c1021959a917e08eaf4eb46a8c4c8d1bec04e2c00,
67a348e256d908eb695d15ee0d869efef2bcf9f0fea646e788f967abbc0464dd,
edde0178045133eb03ef4d1ad8b978a56ee80ec4eab8830d6bc6c08003138841
..6657d3c449d9398cc4385d1c8a2bb19bcf61ff086e5a6c477a0302ce270d1abf,
e22ec3e4a2a4132237eb8a62bcc5ed864593cfde08e53b1632ecd3245761c808,
c5fba3b46f755acec221fb5d25642d7de6a77fa6fe9c998a761654161715905a,
83dbb9b66188fa42ee643c268c75dd41226214f3d20768f54bbc66250d13ab4a,
35f8dc0f744d1850513c46b6b4640716cbb4643da26cfe67f8c701486e0b4cae,
6938267ebdb030e99fe5f6fae02b884cfca227fc785a3f4706c65c882b53710d,
5e687eff531b40401a12d0b0e96c61f441880f96f52c693252142dc954025800,
\end{verbatim}

\hypertarget{vector-4-1}{%
\subsubsection{Vector 4}\label{vector-4-1}}

\begin{verbatim}
b56cc204f1b6c2323709012cb16c72f3021035ce935fbe69b600a88d842c7407,
dc2de7312c2850a9f6c103289c64fbd76e2ebd2fa8b5734708eb2c76c0fb2d99,
73616d706c65,
-,
672e8c7a8e6d3eca67df38f11d50f3d7dbb26fa8e27565a5424e6f8ac4555dcc,
4d3e0524fc59374f1fdad8e471c695469b45ecf69c1de85c6c1230e888dd4cbe,
36127f8aee7c61048984f0a208bf6d334db9dacbeeeef9ff2d17117e81232832
..1462eb3ef602f5911d77ab11f815eb4154ba95c934e414198ef000a61b4de31a,
755610da34cc224fbe60ce5e42add2ea6b272ef466aef18c13497363116d1c03,
f6ee745282e5b3a4fa7d73f64dd906c437b11b9b49dc96dc92dde94bcd315ae5,
61c5ff3a1e6a91008dfe492e4afd1f12b6c0e9f23b9d6d860b1f5ba456792982,
b9fa51c75d278d95f2ccace9609b28ec137b244c8b7d1523b16ed07c8e24b8e4,
ebe86ea22e8eceffa1a3569af288baa556b5b98e1fb9284cbed2ddae943b8204,
9f68cf2e7a4c304db0f0cbff8e98472743c96e0b4098901ef8709ed9a159d715,
\end{verbatim}

\hypertarget{vector-5-1}{%
\subsubsection{Vector 5}\label{vector-5-1}}

\begin{verbatim}
da36359bf1bfd1694d3ed359e7340bd02a6a5e54827d94db1384df29f5bdd302,
decb0151cbeb49f76f10419ab6a96242bdc87baac8a474e5161123de4304ac29,
42616e646572736e6174636820766563746f72,
-,
4315192d2ce9e52ceb449a6b4da7f7e6636e53592c7f5e236763e21e9bac24c7,
9508104b820469687488d83f729288d9f70fc0523318beff44a47da10d490b3c,
4ee61f3c000544aa48c565e143e05c6501a623bdbf02a0a408b97433660b4907
..715f75890cc0e45cdd7116e3da15b15c3c637782e8e05d05c0d5895e5fe583d1,
fb0123dd6317dbd379afccded247f75b3c1c2e32b86eaa9d6c9d0eb5bef07919,
32ba00c4c2f419a93f09c788c07b24874d7de3037982d5faf49d4f25f54d82a3,
e22ac51b815239ed6f1ec8651165b70f86537f94189a4fcb7a93238698406424,
311f94e886825c80a30fd44535be37218501bd072afcbc1298f8fba6c3e3c96d,
4114280954dba0fbf36160f4fa9d45334a8bae641f328897a6c392857068e215,
1cf6dc8cab4b247dd483c2d8da29019ef4f9174bd4d07d8c6b056daacf2e2605,
\end{verbatim}

\hypertarget{vector-6-1}{%
\subsubsection{Vector 6}\label{vector-6-1}}

\begin{verbatim}
da36359bf1bfd1694d3ed359e7340bd02a6a5e54827d94db1384df29f5bdd302,
decb0151cbeb49f76f10419ab6a96242bdc87baac8a474e5161123de4304ac29,
42616e646572736e6174636820766563746f72,
1f42,
4315192d2ce9e52ceb449a6b4da7f7e6636e53592c7f5e236763e21e9bac24c7,
9508104b820469687488d83f729288d9f70fc0523318beff44a47da10d490b3c,
4ee61f3c000544aa48c565e143e05c6501a623bdbf02a0a408b97433660b4907
..715f75890cc0e45cdd7116e3da15b15c3c637782e8e05d05c0d5895e5fe583d1,
0752c5b639dffedf9a66ac111a765d3e9c4cfac9c8b26cc5af6d524967afdf0a,
0168b0c1a00c5617cef0c0a35807d91bc0ecb1212b1cf02465f10494d085804e,
76bddc2f9951bb308efdde9b0bdf3ac3ab3263d5a1af6f8276ec5d894ddd36d8,
311f94e886825c80a30fd44535be37218501bd072afcbc1298f8fba6c3e3c96d,
0b57ac74adf66a619b3b993b7dc517af3211e2ae19b4a26dc73e4a407d733307,
8c2f374814f50ebf2b7e5760e4ab631e2c962b1e7b5e7147c06ea83397b2dd09,
\end{verbatim}

\hypertarget{vector-7-1}{%
\subsubsection{Vector 7}\label{vector-7-1}}

\begin{verbatim}
35b877a25c394512292b82bdf8468e98eaf03c79c7fc9d53546dadc5fb75b500,
b0e1f208f9d6e5b310b92014ea7ef3011e649dab038804759f3766e01029d623,
42616e646572736e6174636820766563746f72,
1f42,
4315192d2ce9e52ceb449a6b4da7f7e6636e53592c7f5e236763e21e9bac24c7,
6d1dd583bea262323c7dc9e94e57a472e09874e435719010eeafae503c433f16,
09106f062ac07846f3f841f64765527b333575143483855d633f99ccc2e8e306
..e6239ff79a1272cff931e8d0ac6c390328486329118ad40a18b85184da1837ff,
462ae9ad651e5caf11247b989fecb5f2b1729479c33b9133388d14fa35dbbd0c,
084fd5e94e3d47a4d82e14e15ea2ab7c90b13702de64b2085a920fddb4032b32,
2112b29dfd39ec3d6dab9e57ea6a8a8c890e4ab2483c371cdaca04a0ca5fb38a,
5a02419120b814a5c81d67096aac728ee9bda5ddf9451cf554d871462a04831a,
34b415a6d9f217dd3207a0d1a09d8545db20649fdc6fbd60e9939da0b326cd03,
c7d348140d3cd6d062246e0c6cd36b22736b94c68b9501aabfd90a01d2a4a116,
\end{verbatim}

\hypertarget{a.3.-ring-vrf-test-vectors}{%
\subsection{A.3. Ring VRF Test
Vectors}\label{a.3.-ring-vrf-test-vectors}}

KZG SRS parameters are derived from Zcash BLS12-381
\href{https://zfnd.org/conclusion-of-the-powers-of-tau-ceremony}{powers
of tau ceremony}.

The evaluations for the ZK domain items, specifically the evaluations of
the last three items in the evaluation domain \(\mathbb{D}\), are set to
0 rather than being randomly generated.

Schema:

\begin{verbatim}
sk (x): Secret key,
pk (Y): Public key,
in (alpha): Input octet-string,
ad: Additional data octet-string,
h (I): VRF input point,
gamma (O): VRF output point,
out (beta): VRF output octet string,
blinding: Blinding factor,
proof_pk_com (Y^-): Pedersen proof public key commitment,
proof_r: Pedersen proof 'R' component,
proof_ok: Pedersen proof 'O_k' component,
proof_s: Pedersen proof 's' component,
proof_sb: Pedersen proof 's_b' component,
ring_pks: Ring public keys,
ring_pks_com: Ring public keys commitment,
ring_proof: Ring proof
\end{verbatim}

\hypertarget{vector-1-2}{%
\subsubsection{Vector 1}\label{vector-1-2}}

\begin{verbatim}
3d6406500d4009fdf2604546093665911e753f2213570a29521fd88bc30ede18,
a1b1da71cc4682e159b7da23050d8b6261eb11a3247c89b07ef56ccd002fd38b,
-,
-,
c5eaf38334836d4b10e05d2c1021959a917e08eaf4eb46a8c4c8d1bec04e2c00,
e7aa5154103450f0a0525a36a441f827296ee489ef30ed8787cff8df1bef223f,
fdeb377a4ffd7f95ebe48e5b43a88d069ce62188e49493500315ad55ee04d744
..2b93c4c91d5475370e9380496f4bc0b838c2483bce4e133c6f18b0adbb9e4722,
01371ac62e04d1faaadbebaa686aaf122143e2cda23aacbaa4796d206779a501,
ba4107f3bce947c7f61b97efe75d6a20bbea98d6813657d00aa20081befcb325,
d2c7b026c5e44c7174da17e557d4688af333224513bd08794ed87848161a594d,
ac57ce6a53a887fc59b6aa73d8ff0e718b49bd9407a627ae0e9b9e7c5d0d175b,
7dd20b189167b3815c37b10572612491aa799b9275ba378e5e70bf200b43a210,
ace0f2cfa446cbb32b57945f233ebd6b02b5b86d325c8c6901a23f588eaaa70a,
7b32d917d5aa771d493c47b0e096886827cd056c82dbdba19e60baa8b2c60313
..d3b1bdb321123449c6e89d310bc6b7f654315eb471c84778353ce08b951ad471
..561fdb0dcfb8bd443718b942f82fe717238cbcf8d12b8d22861c8a09a984a3c5
..a1b1da71cc4682e159b7da23050d8b6261eb11a3247c89b07ef56ccd002fd38b
..4fd11f89c2a1aaefe856bb1c5d4a1fad73f4de5e41804ca2c17ba26d6e10050c
..86d06ee2c70da6cf2da2a828d8a9d8ef755ad6e580e838359a10accb086ae437
..ad6fdeda0dde0a57c51d3226b87e3795e6474393772da46101fd597fbd456c1b
..3f9dc0c4f67f207974123830c2d66988fb3fb44becbbba5a64143f376edc51d9,
8585ac6099562ea5664f9fe7e8341211041a0cba315d0111e7b94b7fd65f5a34
..307926345caf5a1190009d41f0b308a798ab7aa81fae20c57fd0f4b081bea66b
..7b0ef60f85984f11da5b2b58859cabba710160723aef70c3f25d6fa949ba1f3e
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
98bc465cdf55ee0799bc25a80724d02bb2471cd7d065d9bd53a3a7e3416051f6
..e3686f7c6464c364b9f2b0f15750426a9107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..b963277560726396dcc3ec97104b0b48fdeb6d3921461881f8cc342990b77d9d
..925bf24c15aa4b6f4ca59c78e4ac849d8daa2da7bd24785faacfbfd36110b75d
..0bdc93defac989c5b88d7e55f3defb8e1bf938ce493a9fa336f9c63b21726a90
..70ef3669c72fb9b9c003c923eaab916488c10f8418a96793583b5aeb0302c65e
..75f5580c2d84227b9f4ea299ff1de10365c7d3f94a4e1fdb00c056a07ce3d73e
..10fe58fb76e138329f7c2dae3d1bfca57050f1025d64ab221216ca7f12bd3425
..8afa204abf111514b9299887160c057ebfee0fd266c86493a2b983dcbedaf803
..ed7442c66e678fbec847b34a71681de1650891a0b48fa973947b19445c2b5c18
..361e032b1e22d7df2f9f638c7fab1b4d5766a44de55f805f9e8fbca678659a15
..42eb3b56684fd710350f4fa882d5b4fc4a515a17c6eba38d8cbc37f3ff07d65b
..92328d3248e72123ee131600c4242a066f9236417e8e0836dcb02d42903966e6
..2e7e5e27261f3f3c86465e8b7bcedbccee3fb2a7588f90f8cfe2a9ad13f70e22
..b7cd5e9a7123e52adc24c902a400e82ab10b2c565d21579834816dcb5b628241
..e37b300587ba13a1a760890c1a190393d0364d5e09919b89f5aa63e683091038
..b17c39c9c921c9c8635b5e09600d99ca2f0b3e702370d74c5fbcb2c1cebbfb6c
..4241fbe95414022fd41e412f7549e559,
\end{verbatim}

\hypertarget{vector-2-2}{%
\subsubsection{Vector 2}\label{vector-2-2}}

\begin{verbatim}
8b9063872331dda4c3c282f7d813fb3c13e7339b7dc9635fdc764e32cc57cb15,
5ebfe047f421e1a3e1d9bbb163839812657bbb3e4ffe9856a725b2b405844cf3,
0a,
-,
8c1d1425374f01d86b23bfeab770c60b58d2eeb9afc5900c8b8a918d09a6086b,
60f32f5ad3e9694b82ccc0a735edb2f940f757ab333cc5f7b0a41158b80f574f,
44f3728bc5ad550aeeb89f8db340b2fceffc946be3e2d8c5d99b47c1fce344b3
..c7fcee223a9b29a64fe4a86a9994784bc165bb0fba03ca0a493f75bee89a0946,
99ff52abf49d67c4303ac4a8a00984d04c06388f5f836ebd37031f0e76245815,
a663bfbd422eaa3e8abf8023d740d64da2581768a5d8757d5fd4060bd3783aed,
6b6d6288147c9584e4441c1e7aea78b90024f915530c209b27f8cac1bed2c140,
fc8770c209212640742d53e2f40e5c30fffae574f90fdc670ff11a1127586c03,
a09e060423f8faa53d1e16ce0b24cc759ee77c3ceb0c3fe74ba34fb1d9d2a108,
e776fd83c7c92dcb56f0be6975bd5bb10c11a6b5f383099bcc81886ae9e10f17,
7b32d917d5aa771d493c47b0e096886827cd056c82dbdba19e60baa8b2c60313
..d3b1bdb321123449c6e89d310bc6b7f654315eb471c84778353ce08b951ad471
..561fdb0dcfb8bd443718b942f82fe717238cbcf8d12b8d22861c8a09a984a3c5
..5ebfe047f421e1a3e1d9bbb163839812657bbb3e4ffe9856a725b2b405844cf3
..4fd11f89c2a1aaefe856bb1c5d4a1fad73f4de5e41804ca2c17ba26d6e10050c
..86d06ee2c70da6cf2da2a828d8a9d8ef755ad6e580e838359a10accb086ae437
..ad6fdeda0dde0a57c51d3226b87e3795e6474393772da46101fd597fbd456c1b
..3f9dc0c4f67f207974123830c2d66988fb3fb44becbbba5a64143f376edc51d9,
b4e3a243bd2a071f5f86235cc44c256dde121d81dab24728a80fdce960dbb7f0
..4b200716d9f7e544917818755ba84a8d8b118ab6490254a14e3f7ece07fcb1a5
..a0651c519dbf3461ae1b1187326d0e067cd7f1d1661533b93da573178dd507fa
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
a57818b60d8fc54695a66b49a627b158a2f4141c696f0ac41b16831021e0ce56
..04aaa76fab504c106e4a50621adcbeeb9107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..974fa9413c8a09bb9438f4933029f92d167dc6716d2bffb1abd6360fcf15e009
..4a2d7ed4f24cffd6a5a6340bd6f5073aa04a1ac35809d1f2df296efaab317a82
..bdc83664d556dd01ebb2ec4456ff86455b3ee187fc32d5fc2e937f3d65f94c9e
..ac83bc5fcd4c787c2c0a7df353bef15702655779ce6a288a20a000426f506771
..1ab696a2dbc6bc97bf359a4940407ee69d94d6a312136750ad4ed76b83156211
..fdfd59f3d278aaa8e55fe78a3b78f64812b8fa4078e5bd78b07b06a587006372
..18ebb14f18a0f88bff192ab7c1c94744cad100408931c0b77f5e29f218625a47
..ad575c2e470ceba798e4a47d7df93f284fe7b145bc180a4b3637d65f421f4216
..55b422d4534baf68f6b55f7ed78279f4b10635718919ab63fbc138051a955638
..985a8b48c70f6ae7c57b22ac0973462781fda6d9ba8fe1d6e15ecb5c78791868
..b944d355fada180edde22eab8f9dc3d04693472f2c894c75a91637886a33e47e
..e147c161d65a579d54532271ec85bfe3715cbc74ef6804b6e0ad3f5d7655aaf9
..f7783d82c1080e7d0f3c0691c825312e91e3554c2f6eaefed2fcb3a4c1a0a466
..87c15821df2073d6d21227dc8a1ccb567a7e36298bda2d77a9c0d980fa0af39a
..8f4190c1dee0b208675707d8dc2b672496a6426426006840be1a2876d74b2477
..971d05223e912dfa940a1ebba2d2b195,
\end{verbatim}

\hypertarget{vector-3-2}{%
\subsubsection{Vector 3}\label{vector-3-2}}

\begin{verbatim}
6db187202f69e627e432296ae1d0f166ae6ac3c1222585b6ceae80ea07670b14,
9d97151298a5339866ddd3539d16696e19e6b68ac731562c807fe63a1ca49506,
-,
0b8c,
c5eaf38334836d4b10e05d2c1021959a917e08eaf4eb46a8c4c8d1bec04e2c00,
67a348e256d908eb695d15ee0d869efef2bcf9f0fea646e788f967abbc0464dd,
edde0178045133eb03ef4d1ad8b978a56ee80ec4eab8830d6bc6c08003138841
..6657d3c449d9398cc4385d1c8a2bb19bcf61ff086e5a6c477a0302ce270d1abf,
e22ec3e4a2a4132237eb8a62bcc5ed864593cfde08e53b1632ecd3245761c808,
c5fba3b46f755acec221fb5d25642d7de6a77fa6fe9c998a761654161715905a,
83dbb9b66188fa42ee643c268c75dd41226214f3d20768f54bbc66250d13ab4a,
35f8dc0f744d1850513c46b6b4640716cbb4643da26cfe67f8c701486e0b4cae,
6938267ebdb030e99fe5f6fae02b884cfca227fc785a3f4706c65c882b53710d,
5e687eff531b40401a12d0b0e96c61f441880f96f52c693252142dc954025800,
7b32d917d5aa771d493c47b0e096886827cd056c82dbdba19e60baa8b2c60313
..d3b1bdb321123449c6e89d310bc6b7f654315eb471c84778353ce08b951ad471
..561fdb0dcfb8bd443718b942f82fe717238cbcf8d12b8d22861c8a09a984a3c5
..9d97151298a5339866ddd3539d16696e19e6b68ac731562c807fe63a1ca49506
..4fd11f89c2a1aaefe856bb1c5d4a1fad73f4de5e41804ca2c17ba26d6e10050c
..86d06ee2c70da6cf2da2a828d8a9d8ef755ad6e580e838359a10accb086ae437
..ad6fdeda0dde0a57c51d3226b87e3795e6474393772da46101fd597fbd456c1b
..3f9dc0c4f67f207974123830c2d66988fb3fb44becbbba5a64143f376edc51d9,
92fcb8ab0744f096dd89a2ad6ac1b107b4d9cdc73ca0dc052a58c39159a70738
..ead532e9a486ef01a7da94d0528936c581a14f0412583e0b8d42caaaf55435ab
..5107512cc28f0794e2a23e9036b77188dec6d4e6a366dd885a84059c90ca7b34
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
a28c6420603f4cd2efd457092ef74585f78eeae389e2ffabf58b9f9dd14ec4db
..9ffe14be02b7376f6ae7959e11ce1e559107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..8e595075b105d891226a1aa4dc46367f42eda32962c94174be6ba3966bdb3a8f
..e64d56b3d6982a215be10168daa29bd7b50bf0de281b7bc18b6f3fcd558144d5
..6f4b8df9d86cebc9eb5796f06a92c9df99abb88e0fad4dbeb4e307e1abc2a46d
..a80fb683491febcaf31b0292231d6e0225f913a4beae87b0483d6198c6723013
..a4c39ef2db171e97c04ffdde83e73e5433b78c5bb335e2038145417fb9751469
..a9e72fa2d357dd477d157056f341141e8bf18f92ccfb7372f6e3cf0897097122
..c6accac6e8762d40cc59b322c0ea00fdb99e029d5b4e5c1e456b4550d0a49618
..482e934d0be9c6ba70f939fd8262f5151007a69276b8ce87cf835d9185384157
..c725a75a8d05df44f961c80c0308641af052ad24a8057d7dae25eaee7382c312
..26998334e7cd780e64f262ab051b05eb850063603ff137156f1cf36972ca1305
..b531a040dbcc4f923014b15f2c32d6db7e5dd3b9b5180f30132953588c8d173a
..2208231d2194e6ee27c5301c3b7ced5c153682335e2de310a635249ed3ce7f61
..53c0399bb392b9a6fafccc1e334f9959b63742069b16b182da19a39249341b49
..569226aca9bc4103d814fd55bf1d733fd20168f0b5a6a8a6a4a1370abcaf5766
..b2ab0000c9cf169c3a0665500dcb4b24816d2b98b3e069ae90a9c9a0bc032b19
..e6679979530209333d41af3afd7cb8a9,
\end{verbatim}

\hypertarget{vector-4-2}{%
\subsubsection{Vector 4}\label{vector-4-2}}

\begin{verbatim}
b56cc204f1b6c2323709012cb16c72f3021035ce935fbe69b600a88d842c7407,
dc2de7312c2850a9f6c103289c64fbd76e2ebd2fa8b5734708eb2c76c0fb2d99,
73616d706c65,
-,
672e8c7a8e6d3eca67df38f11d50f3d7dbb26fa8e27565a5424e6f8ac4555dcc,
4d3e0524fc59374f1fdad8e471c695469b45ecf69c1de85c6c1230e888dd4cbe,
36127f8aee7c61048984f0a208bf6d334db9dacbeeeef9ff2d17117e81232832
..1462eb3ef602f5911d77ab11f815eb4154ba95c934e414198ef000a61b4de31a,
755610da34cc224fbe60ce5e42add2ea6b272ef466aef18c13497363116d1c03,
f6ee745282e5b3a4fa7d73f64dd906c437b11b9b49dc96dc92dde94bcd315ae5,
61c5ff3a1e6a91008dfe492e4afd1f12b6c0e9f23b9d6d860b1f5ba456792982,
b9fa51c75d278d95f2ccace9609b28ec137b244c8b7d1523b16ed07c8e24b8e4,
ebe86ea22e8eceffa1a3569af288baa556b5b98e1fb9284cbed2ddae943b8204,
9f68cf2e7a4c304db0f0cbff8e98472743c96e0b4098901ef8709ed9a159d715,
7b32d917d5aa771d493c47b0e096886827cd056c82dbdba19e60baa8b2c60313
..d3b1bdb321123449c6e89d310bc6b7f654315eb471c84778353ce08b951ad471
..561fdb0dcfb8bd443718b942f82fe717238cbcf8d12b8d22861c8a09a984a3c5
..dc2de7312c2850a9f6c103289c64fbd76e2ebd2fa8b5734708eb2c76c0fb2d99
..4fd11f89c2a1aaefe856bb1c5d4a1fad73f4de5e41804ca2c17ba26d6e10050c
..86d06ee2c70da6cf2da2a828d8a9d8ef755ad6e580e838359a10accb086ae437
..ad6fdeda0dde0a57c51d3226b87e3795e6474393772da46101fd597fbd456c1b
..3f9dc0c4f67f207974123830c2d66988fb3fb44becbbba5a64143f376edc51d9,
8244a8ddb4ad3e179ef64ee96820a4d5bf5f9f58a8966c27718ee5eacf78e8b3
..75e5b7a7842f18f41a66ca98c80e7d9583933dfa0c034e4a83ba17fe6df67efe
..db8805d2870a22f3e44de5ec8c28e86ad70f53fec494b299df2b91b960859ac6
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
84c37dff677bda19d7ce202500196edeabb794b0e0970b52a76061d9fc9c396f
..5d6671db8da091886f4f894775b49a549107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..9486bd36ca69d989630ce92c49627dc3d964431ec7d21ef1b8d4cf2d8272141b
..1b54336c09271c3a9ffef3750422f660b6a924d8d0378d192477e07228a2823e
..0137c04aced67d560a382ded6abe3b32534e21a80211510f39391982302bb842
..c9dcc5df2038def32807047669d6e2a3741d52d514cb943ab709bec92e932354
..4859e2f996b621eff6a9f6bad0a18f63d90100bd383ad82d9a4d85d910a3b161
..fb4e26e81c95baa12f9d3e15f22123a486afac84ce12e36d5ded93f0ecdfac2c
..75389f22cb33801f5ebac75d2001d943a23fa663420d3959fef32d7f18a8a763
..c264b506bc6f268c758d88db5b392dd8bc6a5997a6b5c3555a6d7e4b2d081b0b
..27e6d657655de752bbabe2c3f54ddbe7e8d00a38cbc7ddf234e7bff36052c76f
..ba3e79a73a529120303e7a10ec77dc83eabe405c9b5556d8aa7dd578afec5648
..ae7f2b3a3632ae9ff5e994e12b5c1e7c98491793162992bd64c433bbd4bb74b0
..bd8f0b6bc5944621f0c489c732b1b131c07c269f5bffae27a14d79ee352fd537
..e2aa4b30d9664e37eae122cb5e534515add39d786bbdcf207744ef8d48b71a37
..2bea5f21e05d37fa05129f48a09a7e05dbc1799f9d974326aa188b4bf162b74c
..81916f3150ed4e21e9d6f51be34e6d55eb74ab4585f5f4277b75b19ffde02ff0
..38d08ae2ea05bb9c0ce809b85ce43a6d,
\end{verbatim}

\hypertarget{vector-5-2}{%
\subsubsection{Vector 5}\label{vector-5-2}}

\begin{verbatim}
da36359bf1bfd1694d3ed359e7340bd02a6a5e54827d94db1384df29f5bdd302,
decb0151cbeb49f76f10419ab6a96242bdc87baac8a474e5161123de4304ac29,
42616e646572736e6174636820766563746f72,
-,
4315192d2ce9e52ceb449a6b4da7f7e6636e53592c7f5e236763e21e9bac24c7,
9508104b820469687488d83f729288d9f70fc0523318beff44a47da10d490b3c,
4ee61f3c000544aa48c565e143e05c6501a623bdbf02a0a408b97433660b4907
..715f75890cc0e45cdd7116e3da15b15c3c637782e8e05d05c0d5895e5fe583d1,
fb0123dd6317dbd379afccded247f75b3c1c2e32b86eaa9d6c9d0eb5bef07919,
32ba00c4c2f419a93f09c788c07b24874d7de3037982d5faf49d4f25f54d82a3,
e22ac51b815239ed6f1ec8651165b70f86537f94189a4fcb7a93238698406424,
311f94e886825c80a30fd44535be37218501bd072afcbc1298f8fba6c3e3c96d,
4114280954dba0fbf36160f4fa9d45334a8bae641f328897a6c392857068e215,
1cf6dc8cab4b247dd483c2d8da29019ef4f9174bd4d07d8c6b056daacf2e2605,
7b32d917d5aa771d493c47b0e096886827cd056c82dbdba19e60baa8b2c60313
..d3b1bdb321123449c6e89d310bc6b7f654315eb471c84778353ce08b951ad471
..561fdb0dcfb8bd443718b942f82fe717238cbcf8d12b8d22861c8a09a984a3c5
..decb0151cbeb49f76f10419ab6a96242bdc87baac8a474e5161123de4304ac29
..4fd11f89c2a1aaefe856bb1c5d4a1fad73f4de5e41804ca2c17ba26d6e10050c
..86d06ee2c70da6cf2da2a828d8a9d8ef755ad6e580e838359a10accb086ae437
..ad6fdeda0dde0a57c51d3226b87e3795e6474393772da46101fd597fbd456c1b
..3f9dc0c4f67f207974123830c2d66988fb3fb44becbbba5a64143f376edc51d9,
8610d2fbb61e947c8f465e786fbc6c313b7c48cd7e2d34901159e089f35f7cd5
..96da6874c6c41ce429dfb6fbae200225add78616a315b002850ce42882c89051
..e70ab00aefa42b12b65104635f47a96dd459467bc57a1fcf8457569cd98ec3b5
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
a7185a7a63812926137b53a4776569fe2323e84689e9e2523e03d3c61beb0427
..7bde2c4a2a5e6acecbbfe1c09f16f9899107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..87727d3884b5caa0bd5b390535a48e6941a7084eeb3246b338f9c739a738c12c
..30414adac432c2fe836d009350bf49e289c9102bb09eae0ec1ab7ffb6b4a51e4
..35ff7d867dd6a3815c3c223dd94218e4b2bf7569c4a37ee31c8d6a2179637707
..0f915f9bc2f70f3db381cf3c32378d5bdc2579dfef6465a54db364f89be7fc17
..80bdeac9cc164410ca204ad4ee0780597d68697baaec0862be6a3c4428760c3a
..18177f4e59c419358c21da272455f7e6965205ddee5610f5eab596c50e1ba856
..6bca75a8f9fdecdc7ae43ed6db8be786a8e85c282139cfc16bc524ff875f0a22
..377accfcc811925f95b00ab1b83f71b37b28e31329b0824e070a200198ed3c1f
..b0ac496f619d8aca058ee5818c863aca4912a83f9734fa7682ea68b1f0794d23
..9335896b4720f66642d8250ccc49db377488bd70f1dfa9b87eb78f19a5a06a55
..980716c6fb07020dd3b0081bfffd5e0f2ec004ce9dd9e2c621a03c17308a0a3c
..a410da3dabb59566accfb66258f65c024e415e17e36bbc6d1320d8c080885aed
..a74d59a0c39a6c00447075e512078933b5524e16562425e7c8908ed74af101c6
..7a1117b96a82af44aedd74c6864f1b3d47acc88327813ad118b2e89063b847d8
..ab2b4b33c024302ac3dbbce0226e57dc93cceed51853a1c507f9077018a01326
..d7e9badcb2d106d1ff760b9e3b8d9c22,
\end{verbatim}

\hypertarget{vector-6-2}{%
\subsubsection{Vector 6}\label{vector-6-2}}

\begin{verbatim}
da36359bf1bfd1694d3ed359e7340bd02a6a5e54827d94db1384df29f5bdd302,
decb0151cbeb49f76f10419ab6a96242bdc87baac8a474e5161123de4304ac29,
42616e646572736e6174636820766563746f72,
1f42,
4315192d2ce9e52ceb449a6b4da7f7e6636e53592c7f5e236763e21e9bac24c7,
9508104b820469687488d83f729288d9f70fc0523318beff44a47da10d490b3c,
4ee61f3c000544aa48c565e143e05c6501a623bdbf02a0a408b97433660b4907
..715f75890cc0e45cdd7116e3da15b15c3c637782e8e05d05c0d5895e5fe583d1,
0752c5b639dffedf9a66ac111a765d3e9c4cfac9c8b26cc5af6d524967afdf0a,
0168b0c1a00c5617cef0c0a35807d91bc0ecb1212b1cf02465f10494d085804e,
76bddc2f9951bb308efdde9b0bdf3ac3ab3263d5a1af6f8276ec5d894ddd36d8,
311f94e886825c80a30fd44535be37218501bd072afcbc1298f8fba6c3e3c96d,
0b57ac74adf66a619b3b993b7dc517af3211e2ae19b4a26dc73e4a407d733307,
8c2f374814f50ebf2b7e5760e4ab631e2c962b1e7b5e7147c06ea83397b2dd09,
7b32d917d5aa771d493c47b0e096886827cd056c82dbdba19e60baa8b2c60313
..d3b1bdb321123449c6e89d310bc6b7f654315eb471c84778353ce08b951ad471
..561fdb0dcfb8bd443718b942f82fe717238cbcf8d12b8d22861c8a09a984a3c5
..decb0151cbeb49f76f10419ab6a96242bdc87baac8a474e5161123de4304ac29
..4fd11f89c2a1aaefe856bb1c5d4a1fad73f4de5e41804ca2c17ba26d6e10050c
..86d06ee2c70da6cf2da2a828d8a9d8ef755ad6e580e838359a10accb086ae437
..ad6fdeda0dde0a57c51d3226b87e3795e6474393772da46101fd597fbd456c1b
..3f9dc0c4f67f207974123830c2d66988fb3fb44becbbba5a64143f376edc51d9,
8610d2fbb61e947c8f465e786fbc6c313b7c48cd7e2d34901159e089f35f7cd5
..96da6874c6c41ce429dfb6fbae200225add78616a315b002850ce42882c89051
..e70ab00aefa42b12b65104635f47a96dd459467bc57a1fcf8457569cd98ec3b5
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
a8455660f642a887ca7bced683e7c5315c6ebff1d7d047ca43f5b5c7b34c244a
..3902f6ca62346b638ed58e4aa5b2c1c29107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..adb0771661f52946f33bf35a831ce26aebf84703f87c6c3898f06588e1b1ac9c
..c9858fbc198168ecff172275f85f369f8f6f928ee069eb34fe712f2d92864744
..13bf2c470be3a123c152cb1f68ce0722e1b24a7370f2723c65ddf273a2009ef1
..c8d3865e4fcfd45dd1b2f8ac3ea838f73032725365da511bf849fd34fd75b651
..c71ffe1afb43a832147dc6536cef74e198a94ec374a4c447a9f006edc0fc2761
..56b3c7b1609008bea6774e8e326bb9d302f150c88f0f639ecfb5670e6b85a364
..b582a54c3bfa2d4f037e2a34c5ae70f25bb2c0891871588495dba3bcb7de1e0c
..2b5fd8d4b0c787d9ed63ea4abcd96ee15b8a59a6c91e1058eceb38316489666c
..44e3047a90603237b374f9793c04b0b414cc4d5951c50aafe8481cb9bf4f826f
..7f6a5caf461d3b016c348a3a625e62459c2b296109e99aa9b2664e3279224467
..8317d286bc2f43e5dd88cbf898b2bc2e6b6a34558595cdb240cb9ce6bab641b0
..9b342da2f992a8ed4a90027c5dc65d9b88bc4fc9c141986411a6709af407d6a7
..1a97eaa4f6310eb0a12212b2f9d7f851a488dcf156fa1cbbd0fbd9c4d676631a
..8b0278f10682d58b6aa11125ac65af82717707af7d99869d5360f7f9a007cae2
..aaad56d9d10d644cd36033bf59d1f0ebec8b2250d09cec0074701b34175977f8
..b0f408d69cd42fb76760595569434ec8,
\end{verbatim}

\hypertarget{vector-7-2}{%
\subsubsection{Vector 7}\label{vector-7-2}}

\begin{verbatim}
35b877a25c394512292b82bdf8468e98eaf03c79c7fc9d53546dadc5fb75b500,
b0e1f208f9d6e5b310b92014ea7ef3011e649dab038804759f3766e01029d623,
42616e646572736e6174636820766563746f72,
1f42,
4315192d2ce9e52ceb449a6b4da7f7e6636e53592c7f5e236763e21e9bac24c7,
6d1dd583bea262323c7dc9e94e57a472e09874e435719010eeafae503c433f16,
09106f062ac07846f3f841f64765527b333575143483855d633f99ccc2e8e306
..e6239ff79a1272cff931e8d0ac6c390328486329118ad40a18b85184da1837ff,
462ae9ad651e5caf11247b989fecb5f2b1729479c33b9133388d14fa35dbbd0c,
084fd5e94e3d47a4d82e14e15ea2ab7c90b13702de64b2085a920fddb4032b32,
2112b29dfd39ec3d6dab9e57ea6a8a8c890e4ab2483c371cdaca04a0ca5fb38a,
5a02419120b814a5c81d67096aac728ee9bda5ddf9451cf554d871462a04831a,
34b415a6d9f217dd3207a0d1a09d8545db20649fdc6fbd60e9939da0b326cd03,
c7d348140d3cd6d062246e0c6cd36b22736b94c68b9501aabfd90a01d2a4a116,
7b32d917d5aa771d493c47b0e096886827cd056c82dbdba19e60baa8b2c60313
..d3b1bdb321123449c6e89d310bc6b7f654315eb471c84778353ce08b951ad471
..561fdb0dcfb8bd443718b942f82fe717238cbcf8d12b8d22861c8a09a984a3c5
..b0e1f208f9d6e5b310b92014ea7ef3011e649dab038804759f3766e01029d623
..4fd11f89c2a1aaefe856bb1c5d4a1fad73f4de5e41804ca2c17ba26d6e10050c
..86d06ee2c70da6cf2da2a828d8a9d8ef755ad6e580e838359a10accb086ae437
..ad6fdeda0dde0a57c51d3226b87e3795e6474393772da46101fd597fbd456c1b
..3f9dc0c4f67f207974123830c2d66988fb3fb44becbbba5a64143f376edc51d9,
a47a711324657bc55044ac86ea4ad6b0eea14da1f1110bddee63b9952b4fe115
..96d1fa7393aaf74db98ead09eaaae769a741e49588ba12084297525668de99ce
..218c698ed2e2ccdad5a7e09e5b36d59e4a81424e5f1dddaa5c423a5f01044653
..92e630ae2b14e758ab0960e372172203f4c9a41777dadd529971d7ab9d23ab29
..fe0e9c85ec450505dde7f5ac038274cf,
88a7fc8a8ae7d295bdd26553b06d298c7d7fdb3f08746aba8e3312d78254a201
..3d4cd3bea7b62156b5a5b0a42e7e45179107bd20fe94a01157764aab5f300d7e
..2fcba2178cb80851890a656d89550d0bebf60cca8c23575011d2f37cdc06dcdd
..aaa9a1a2a33ed9ee4f1d972536a4bf8ba67fabaab6beabafb8f99124b3044b29
..110260211b8cc3632991f76a44198e65abf09fe2f01531c4e2cd93417d89bb8b
..7cc7ac5327b1d9b2bc46f4452801b14f2409ff287a1fd5b485a5aea74a33fba0
..fdc765422c242bf0a765a50930c4510b64530b8f85a32e41908ca6194edb4d34
..89e3152a964829360901747b0b69c9c3974a4f49704f441a90323e671eb6dd26
..c638841c041ac0cfe5c7e630429bc9cf69427a69399406a0b4433de0aa421919
..62e70922bfed0ad017a8602d4450fe7fa2a2729c1aa961f464ab8a6f5853da0b
..3e19fa83980ba32e85b78afcab6da935501fe747eea29a0e33453a9d0dace04f
..98f54e2b21772110e0a1ffa142eae00fe4012256df6f0f4cf18ad79b17a1aa2b
..cbf613403513ca504eec4cce2cb24fde7a856fb6c7d35123a94f1bee0765f039
..b224b9d5c294a9799820a2c0fc3059e045a60bb70e951e7a40c5926c8eac1ffb
..4e0b59700b5f2c1277383b315a2ea28cd012205602e42538d5c68c0cb357d996
..03980c04c048a82010c5a59240f2e127aa2687f790f2d7c205757fb750d5ddbf
..ad709cc0a97252d3ddd2739c722dfb4ed4254f3af3b74563653de23d71efb8c6
..849dddc46277dd665f3d5eabdcda0039b199ce71b3fe8e0730a8b958ff7ccac5
..b546bd2cbfe33ac661da1024564295b3,
\end{verbatim}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-RFC9381}{}}%
\CSLLeftMargin{1. }
\CSLRightInline{Internet Engineering Task Force
\emph{\href{https://datatracker.ietf.org/doc/rfc9381}{{Verifiable Random
Functions}}}; {RFC Editor}, 2023;}

\leavevmode\vadjust pre{\hypertarget{ref-BCHSV23}{}}%
\CSLLeftMargin{2. }
\CSLRightInline{Burdges, J.; Ciobotaru, O.; Alper, H.K.; Stewart, A.;
Vasilyev, S. \href{https://eprint.iacr.org/2023/002}{Ring Verifiable
Random Functions and Zero-Knowledge Continuations} 2023.}

\leavevmode\vadjust pre{\hypertarget{ref-VG24}{}}%
\CSLLeftMargin{3. }
\CSLRightInline{Vasilyev, S.; Galassi, D.
\href{https://github.com/davxy/ring-proof-spec}{Ring Proof Technical
Specification} 2024.}

\leavevmode\vadjust pre{\hypertarget{ref-MSZ21}{}}%
\CSLLeftMargin{4. }
\CSLRightInline{Masson, S.; Sanso, A.; Zhang, Z.
\href{https://eprint.iacr.org/2021/1152}{Bandersnatch: A Fast Elliptic
Curve Built over the Bls12-381 Scalar Field} 2021.}

\leavevmode\vadjust pre{\hypertarget{ref-RFC9380}{}}%
\CSLLeftMargin{5. }
\CSLRightInline{Internet Engineering Task Force
\emph{\href{https://datatracker.ietf.org/doc/rfc9380}{{Hashing to
Elliptic Curves}}}; {RFC Editor}, 2023;}

\leavevmode\vadjust pre{\hypertarget{ref-RFC6234}{}}%
\CSLLeftMargin{6. }
\CSLRightInline{Internet Engineering Task Force
\emph{\href{https://datatracker.ietf.org/doc/rfc6234}{{US Secure Hash
Algorithms}}}; {RFC Editor}, 2011;}

\end{CSLReferences}

\end{document}
